Generative AI for image reconstruction in Intensity Interferometry: a first attempt

### 2025-04-30 Phase_II/draft/conclusion.tex
edits

Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges associated with Michelson Interferometry in the optical wavelength range.  However, compared to radio-interferometry II faces a significant drawback: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.

>>>>

Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges of very long baseline interferometry in the optical wavelength range.  However, compared to radio-interferometry II faces a significant drawback: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.
